The language of generalization: Probability, vagueness, and interaction

### 2018-03-27 paper/case1-generics.Rmd
address lays eggs 3 component phenomenon

The prior distributions over prevalence are well modeled as a mixture of two Beta distributions and not as a single Beta distribution (Figure\  \@ref(fig:generic-endorsement-priors-figure)B; red vs. blue lines). 
The *Single Beta* model provides a good fit for the *being female* distribution, but overly smooths the other distributions, washing out the latent structure in participants' responses.
One prior that the *mixture of Betas* model does not perfectly capture is the prior distribution over the feature \textsc{lay eggs}.
The empirical distribution is tri-modal, with reliable modes at 0\%, 50\%, and 100\%^[
Similar phenomena have been observed in other prevalence elicitation tasks when the referent-category is fixed [e.g., estimating only the percentage of *robins* that *lay eggs*; @Prasada2013]
]; a simple two-component mixture model has no way to account for such a tri-modal distribution. 
A more complex model (i.e., one with three mixture components) would be necessary to perfectly account for this item. \ndg{but we don't use one because...?}

>>>>

The prior distributions over prevalence are well modeled as a mixture of two Beta distributions and not as a single Beta distribution (Figure\  \@ref(fig:generic-endorsement-priors-figure)B; red vs. blue lines). 
The *Single Beta* model provides a good fit for the *being female* distribution, but overly smooths the other distributions, washing out the latent structure in participants' responses.
One property that the *mixture of Betas* model does not perfectly capture is the prior distribution over the feature *lays eggs*.
The empirical distribution is tri-modal, with reliable modes at 0\%, 50\%, and 100\%; a simple two-component mixture model has no way to account for such a tri-modal distribution.^[
  The third mode at 100\% is not attributable to categories for which all members could be female (e.g., chickens). Instead, it appears that some participants are responding that 100\% of several different kinds of birds (e.g., robins) lay eggs. This may result from participants implicitly only considering female members of the category as relevant to answer a question about a reproductive capactiy like *lays eggs*; this restriction of what enters into the prevalence computation is known as *domain restriction* and has been observed in other prevalence elicitation tasks [e.g., @Prasada2013].
];
A more complex model (i.e., one with three mixture components) would be necessary to perfectly account for this item. 
Using a three-component model for this distribution does not change the resulting model predictions and we maintain the simpler two-component mixture for uniformity.
